---
title: "DROPS | Multi - Genotype Simulation"
author: "Sebastien Lacube"
date: "22 March 2017"
output: html_document
---


```{r "setup", include=FALSE}

knitr::opts_chunk$set(
	message = FALSE,
	warning = FALSE
)

require("knitr")
opts_knit$set(root.dir = "D:/Work/Sims - DROPS")

# Optional :
rm(list=ls())

```

```{r Packages - Sources, message=FALSE, warning=FALSE, include=FALSE}

## Packages ---- 
library(PerformanceAnalytics)
library(Hmisc)
library(dplyr)
library(R.utils)

## Sources ----
source('D:/Work/Sims  - DROPS GxE/5.Scripts/MultiSimFunctions.r')
source('D:/Work/Sims  - DROPS GxE/5.Scripts/Sources.R')
source('D:/Work/R script/Sources/ThermalTime.R', encoding = 'UTF-8')

```

```{r Paths, message=FALSE, warning=FALSE, include=FALSE}

## ---------------
# 1 : APSIM files 
# 2 : Met files 
# 3 : Data files
# 4 : Out files
# 5 : Scripts
# 6 : Docs 
# 7 : Junk
## ---------------


PATHS <- list.dirs(path = "D:/Work/Sims  - DROPS GxE",recursive = FALSE)
SimName <- 'Base_Sims'

PATH.APSIM <- 'D:/APSIM/Apsim76/Model/'

```

# Simulation Report

Simulation of 250+ genotypes of the DROPS panel to test performances of the model for yield around the DROPS network.
  
*Do we simulate correctly genotypes more/less sensitive to VPD ?*

***

```{r Load Base Sim, echo=FALSE, fig.height=2.5, fig.width=2.5, message=FALSE}

# Loading XML file : ----
ApsimFile<-paste(PATHS[1],SimName,sep='/')
ApsimFile<-paste(ApsimFile,'apsim',sep='.')
SimFileTree<-xmlTreeParse(ApsimFile,getDTD = F , useInternalNodes = T)
  
# List of SimNames :
SimulationNameNode<-getNodeSet(SimFileTree, "//simulation")
xattrs <- xpathSApply(SimFileTree, "//*/simulation/@name")
Sims <- data.frame("Title"=xattrs)

```

## Summary  :

- *Sites :* 9 Sites around DROPS network  

- *Genotypes :* DROPS panel (250+)

- *Year :* from 2011 to 2013 

- *Climate :* Actual  

- *Hydric scenario :* Well-watered  

- *Model :* LER model with length/width  

***

## Input parameters :

Maize genotypic parameters :

```{r Load maize parameters, echo=FALSE, message=FALSE, warning=FALSE}

TopNode <- xmlRoot(SimFileTree)
TagNames <- xmlElementsByTagName(TopNode, 'simulation', recursive = FALSE)
TagNames <- TagNames[[1]]
TagNames <- xmlElementsByTagName(TagNames, 'area', recursive = FALSE)
TagNames <- xmlElementsByTagName(TagNames[[1]], 'maize', recursive = FALSE)
TagNames_Csts <- xmlElementsByTagName(TagNames[[1]], 'maizeConstants', recursive = FALSE)
TagNames_Geno <- xmlElementsByTagName(TagNames[[1]], 'maizeGenotype', recursive = FALSE)

# Get genotypic info and parameters : ----
Constants <<- melt(getChildrenStrings(TagNames_Csts[[1]],asVector=F,addNames=T))
Genotype <<- melt(getChildrenStrings(TagNames_Geno[[1]],asVector=F,addNames=T))

colnames(Genotype)     <- c('Parameter','Value') 

```

```{r Load Data Measured to estimate GNmax and PotKernelWeight, echo=FALSE, message=FALSE, warning=FALSE}


## For GN : ---- 
Measured_GN15 <- read.table(paste0(PATHS[3],'/BLUES_KNO.csv'), 
                       sep=";",                                           
                       header=TRUE,dec=".",
                       row.names=NULL,
                       as.is=FALSE, 
                       fill=TRUE)

# Separate data to fit the one we already have (in lines not columns...)
Measured_GN <- gather(Measured_GN15,one_of(colnames(Measured_GN15)[5:33]),key = 'Site',value = 'KNO')
Measured_GN_v2 <- separate(Measured_GN,Site,sep="_",into=c('Site','Year_Scenario'),extra='merge')
Measured_GN_v3 <- separate(Measured_GN_v2,Year_Scenario,sep="_",into=c('Year','Scenario'),extra='merge')
Measured_GN_v4 <- separate(Measured_GN_v3,Site,sep="[.]",into=c('Var','Site'),extra='merge')
Measured_GN_v5 <- select(subset(Measured_GN_v4,Scenario=="watered"),Hybrid_ID,Site,Year,KNO)
Measured_Data_GN <- unite(Measured_GN_v5,Site,Year,col="Title",sep='_')
Measured_Data_GN$Title <- factor(Measured_Data_GN$Title)
levels(Measured_Data_GN$Title) <- c('Martonvasar_2013','Gaillac_2012','Gaillac_2013','Graneros_2013',
                                 'Nerac_2012','Nerac_2013','Caracal_2012','Karlsruhe_2012',
                                 'Karlsruhe_2013','Murony_2013','Karacal_2012',
                                 'Campagnola_2013','Cadriano_2012')
colnames(Measured_Data_GN) <- c("Genotype","Title","M.GrainNo") 


ggplot(Measured_Data_GN,aes(x=reorder(Title,M.GrainNo,FUN=mean,na.rm=T),y=M.GrainNo))+
  geom_boxplot()+
  geom_point(data=subset(Measured_Data_GN,Genotype=='B73_H'),aes(x=Title,y=M.GrainNo),color='red',size=3)+
  labs(x='Environment',y='Grain no.')+
  coord_flip()

## For GY : ----
Measured_GY15 <- read.table(paste0(PATHS[3],'/BLUES_GY15.csv'), 
                       sep=",",                                           
                       header=TRUE,dec=".",
                       row.names=NULL,  
                       as.is=FALSE, 
                       fill=TRUE)

# Separate data to fit the one we already have (in lines not columns...)
Measured_GY <- unite(
                 select(
                   subset(
                     separate(
                        separate(
                          separate(
                            gather(Measured_GY15,
                                   one_of(colnames(Measured_GY15)[5:33]),key = 'Site',value ='Yield'),
                            Site,sep="_",into=c('Site','Year_Scenario'),extra='merge'),
                        Year_Scenario,sep="_",into=c('Year','Scenario'),extra='merge'),
                     Site,sep="[.]",into=c('Var','Site'),extra='merge'),
                   Scenario=="watered"),
                 Hybrid_ID,Site,Year,Yield),
               Site,Year,col="Title",sep='_')

Measured_GY$Title <- factor(Measured_GY$Title)


levels(Measured_GY$Title) <- c('Martonvasar_2013','Gaillac_2012','Gaillac_2013','Graneros_2013',
                                 'Nerac_2012',' Nerac_2013','Caracal_2012','Karlsruhe_2012',
                                 'Karlsruhe_2013','Murony_2013','Karacal_2012',
                                 'Campagnola_2012','Campagnola_2013','Cadriano_2012')
colnames(Measured_GY) <- c("Genotype","Title","M.Yield") 


ggplot(Measured_GY,aes(x=reorder(Title,M.Yield,FUN=mean,na.rm=T),y=M.Yield))+
  geom_boxplot()+
  geom_point(data=subset(Measured_GY,Genotype=='B73_H'),aes(x=Title,y=M.Yield),color='red',size=3)+
  labs(x='Environment',y='yield (t/ha)')+
  coord_flip()



## Merge both Data :
MeasuredYield <- merge(Measured_Data_GN,Measured_GY,by=c('Genotype','Title'))
MeasuredYield$M.Yield.kgha <- MeasuredYield$M.Yield *1000

## Get sowing density : 
SimulationNameNode<-getNodeSet(SimFileTree, "//density")
xattrs <- xpathSApply(SimFileTree, "//density",xmlValue)
xmlValues <- data.frame("Density"=xattrs)
Density <- cbind(xmlValues,Sims)
Density$Density <- as.numeric(as.character(Density$Density))
MeasuredYieldwithDensity <- merge(MeasuredYield,Density,by=c('Title'))

MeasuredYieldwithDensity$KNOplant <- MeasuredYieldwithDensity$M.GrainNo / MeasuredYieldwithDensity$Density

# Get yield per plant in mg/plant ==> convert to get Kernel Weight per plant (mg.kernel)
MeasuredYieldwithDensity$Yieldplant <- 
  (MeasuredYieldwithDensity$M.Yield.kgha / 10000 * 1000 *1000) / MeasuredYieldwithDensity$Density

MeasuredYieldwithDensity$KernelWt <- MeasuredYieldwithDensity$Yieldplant / MeasuredYieldwithDensity$KNOplant

# Get maximum per genotype (which environment ?) :
PotKernelWt <- aggregate(cbind(KernelWt)~Genotype,MeasuredYieldwithDensity,FUN=max,na.rm=T)
GNmax <- aggregate(cbind(KNOplant,M.GrainNo)~Genotype,MeasuredYieldwithDensity,FUN=max,na.rm=T)

PotKernelWt_2 <- select(merge(PotKernelWt,MeasuredYieldwithDensity),Genotype,KernelWt,Title)
colnames(PotKernelWt_2) <- c('Hybrid_ID','potKernelWt','potKernelWt_At')
GNmax_2 <- select(merge(GNmax,MeasuredYieldwithDensity),Genotype,KNOplant,Title)
colnames(GNmax_2) <- c('Hybrid_ID','GNmax','GNmax_At')

GrainParams <- merge(PotKernelWt_2,GNmax_2)
GrainParams_toBind <-  merge(PotKernelWt,GNmax)
colnames(GrainParams_toBind) <- c('Hybrid_ID','potKernelWt','GNmax','GrainNo')
  
write.table(GrainParams_toBind,
            paste0(PATHS[3],'/GrainPotential.csv'),
            sep=";",
            row.names=F)

```

Measured genotypic parameters : 

```{r Load Data parameters, message=FALSE, warning=FALSE, include=FALSE}


## Genetic groups ----
Groups <- read.table(paste0(PATHS[3],'/Admixture6Group.csv'), 
                       sep=";",                                           
                       header=TRUE,dec=".",
                       row.names=NULL,
                       as.is=FALSE, 
                       fill=TRUE)
GenGroups <- subset(Groups,select=c('Hybrid_ID','group'))

## ZA16 Phenology ----
Phenology <- read.table(paste0(PATHS[3],'/ZA16_Phenology_2016-06-28.csv'), 
                       sep=";",                                           
                       header=TRUE,dec=".",
                       row.names=NULL,
                       as.is=FALSE, 
                       fill=TRUE)

Pheno <- subset(Phenology,select=c('Hybrid_ID','Scenario','doy','visi_l','ligul_l'))

Meteo <- read.table(paste0(PATHS[3],'/Meteo_ZA16.csv'), 
                       sep=";",                                           
                       header=TRUE,dec=".",
                       row.names=NULL,
                       as.is=FALSE, 
                       fill=TRUE)

Met <- subset(Meteo,date>=138,select=c('date','heure','tc.moy'))
Met$datehour <- (Met$date+(round(Met$heure/100)/24)+((Met$heure)-round(Met$heure/100)*100)/(60*24))-138
Tht <- ThermalTime('Apsim',Met$date,Met$tc.moy)
Tht$doy <- unique(Met$date)
Pheno_Tht <- merge(Pheno,Tht,by=c('doy'))
PhenoTht <- subset(Pheno_Tht,visi_l!=0 & visi_l<14 & Scenario =='WW' )

OutPhenoPanel <- data.frame(Phyllo = numeric(),Ntip_emerg = numeric(),
                            Ligules = numeric(),Tht_1st_Lig = numeric(),
                            Hybrid_ID=character())

## Calculate Phyllo/Ligules : ----
for (geno in unique(PhenoTht$Hybrid_ID))
{
  DataToTreat <- subset(PhenoTht,Hybrid_ID==geno)
  MyModel_Vis <- lm(data=DataToTreat,formula='visi_l~cumtht')
  MyModel_Lig <- lm(data=DataToTreat,formula='ligul_l~cumtht')
  
  ToBind <-  data.frame(Phyllo = MyModel_Vis$coefficients[2],Ntip_emerg = MyModel_Vis$coefficients[1],
                        Ligules = MyModel_Lig$coefficients[2],
                        Tht_1st_Lig = (1-MyModel_Lig$coefficients[1])/MyModel_Lig$coefficients[2] + 70 ,
                        Hybrid_ID=geno)
  OutPhenoPanel <- rbind(OutPhenoPanel,ToBind)
}


## Correspondance Hybrid_ID vs Code_ID : ----
Hybrids <- read.table(paste0(PATHS[3],'/Hybrids.csv'), 
                       sep=";",                                           
                       header=TRUE,dec=".",
                       row.names=NULL,
                       as.is=FALSE, 
                       fill=TRUE)

## Nfinal: ----
Nfinal <- read.table(paste0(PATHS[3],'/Nfinal.csv'), 
                       sep=";",                                           
                       header=TRUE,dec=".",
                       row.names=NULL,
                       as.is=FALSE, 
                       fill=TRUE)
Nfinal$Nf <- round(Nfinal$NbFF) 
colnames(Nfinal) <- c('Code_ID',"NbFF","Nf")
NfMax <- merge(Nfinal,Hybrids,by=c('Code_ID'))

NfinalStHinx <- read.table('D:/Work/Widths/3.Data/St Martin-ZA16/Nfinal_StMartindeHinx_2016_DROPS-AMAIZING.csv', 
                       sep=";",                                           
                       header=TRUE,dec=".",
                       row.names=NULL,
                       as.is=FALSE, 
                       fill=TRUE)
NfinalStHinx <- melt(NfinalStHinx,measure.vars=colnames(NfinalStHinx)[2:4])
colnames(NfinalStHinx) <- c('Code_ID','Plante','Nfinal_StMartin')
NfinalStHinx <- aggregate(data=NfinalStHinx,Nfinal_StMartin~Code_ID,mean,na.rm=T)
  
MergeNFinal <- merge(NfMax,NfinalStHinx,by='Code_ID')
MergeNFinal$Nff_StMartin <- round(MergeNFinal$Nfinal_StMartin)

ggplot(data=MergeNFinal,aes(x=Nf,y=Nff_StMartin))+
  geom_point()+
  geom_abline(slope=1,intercept=0,color='black')+
  geom_smooth(method='lm',color='blue')+
  scale_x_continuous(limits=c(1,19))+
  scale_y_continuous(limits=c(1,19))

ggplot(data=MergeNFinal,aes(x=NbFF,y=Nfinal_StMartin))+
  geom_point()+
  geom_abline(slope=1,intercept=0,color='black')+
  geom_smooth(method='lm',color='blue')+
  scale_x_continuous(limits=c(1,19))+
  scale_y_continuous(limits=c(1,19))

## Sensitivity to PSI : ----
Sensitivity_PSI <- read.table(paste0(PATHS[3],'/Sensitivity.csv'), 
                       sep=",",                                           
                       header=TRUE,dec=".",
                       row.names=NULL,
                       as.is=FALSE, 
                       fill=TRUE)
SensiPSI <- subset(Sensitivity_PSI,select=c('Genotype','slope'))
colnames(SensiPSI) <- c('Hybrid_ID','c_norm')


## A max : ---- 
a_max <- read.table(paste0(PATHS[3],'/a.csv'), 
                       sep=",",                                           
                       header=TRUE,dec=".",
                       row.names=NULL,
                       as.is=FALSE, 
                       fill=TRUE)

a <- subset(a_max,select=c('Genotype','a'))
a$a_per <- a$a / a$a[which(a$Genotype=='B73_H')] 
a$a_dyn <- a$a_per*4.25 # a B73_H on phenodyn ==4.25 !
colnames(a) <- c('Hybrid_ID','a','aper','adyn')
a_ToBind <- subset(a,select=c('Hybrid_ID','adyn'))

# Response to Tnight Mimi :
# GNij = GN15i + B (Tnightij - 15)
# So the response is : B (Tnightij - 15) :
# The response is also normalized for a RI0 for which there is "no" efect on GN of RADi :
# GNmax we want would be : grain.nb15.seq + [(300-ri.zero.seq)*resp.ri.sequ]
M.Tnight <- read.table(paste0(PATHS[3],'/RespTnight.csv'), 
                       sep=",",                                           
                       header=TRUE,dec=".",
                       row.names=NULL,
                       as.is=FALSE, 
                       fill=TRUE)

M.Tnight$GN15cor <-  M.Tnight$grain.nb15.seq + ((300-M.Tnight$ri.zero.seq)*M.Tnight$resp.ri.sequ)
RespTnight <- select(M.Tnight,Hybrid_ID,resp.tnight.seq,GN15cor,resp.ri.sequ)
colnames(RespTnight) <- c('Hybrid_ID','resp.tnight','GN15cor','resp.Ri')

## Merge to get the last set of parameters :
Params <- merge(NfMax,OutPhenoPanel,all.x=T)[c(1,4:8)]
Params_v2 <- merge(Params,SensiPSI,all.x=T)
#Params_v3 <- merge(Params_v2,GenGroups)
Params_v4 <- merge(Params_v2,a_ToBind,all.x=T,all.y=F)
Params_v4$c <- Params_v4$c_norm*Params_v4$adyn*10
Params_v5 <- merge(Params_v4,GrainParams_toBind,all.x=T,all.y=F)
Params_v6 <- merge(Params_v5,RespTnight,by='Hybrid_ID',all.x=T)

## Maintenant on rajoute SensiRAD : 
SensiRAD <- read.table(paste0(PATHS[3],'/SensiRAD.csv'), 
                       sep=",",                                           
                       header=TRUE,dec=".",
                       row.names=NULL,
                       as.is=FALSE, 
                       fill=TRUE)
colnames(SensiRAD) <- c('Hybrid_ID','Leaf','SensiRAD','Oo')
SensiRAD <- select(SensiRAD,Hybrid_ID,SensiRAD)
Params_v7 <- merge(Params_v6,SensiRAD,by='Hybrid_ID',all.x=T)


## Final set of parameters : ----
Final_Params_Panel <- subset(Params_v7, select=c('Hybrid_ID','Nf','Phyllo',
                                                 'Ntip_emerg','Ligules','Tht_1st_Lig',
                                                 'c','adyn','potKernelWt',
                                                 'GN15cor','GrainNo','resp.tnight',
                                                 'GN15cor','resp.Ri','SensiRAD'))

colnames(Final_Params_Panel) <- c('Hybrid_ID','Nfinal',
                                  'Phyllochron','Leaf_tip_emerg',
                                  'First_LiguloChrone','tt_firstligule_sinceapp',
                                  'c','a',
                                  'potKernelWt','GNmax',
                                  'GrainNoMax','Res.Tnight',
                                  'resp.Ri','GN15cor','SensiRAD')

write.csv(Final_Params_Panel,file ='D:/Work/Sims - DROPS/4.Out/Parameters_DROPS_Panel_ForAPSIM_WithNA.csv')
Final_Params_Panel$b <- (-0.0758*Final_Params_Panel$c)-0.3672

Params_WithoutNAs <- Final_Params_Panel[rowSums(is.na(Final_Params_Panel))<1, ]
Params_WithoutNAs$b <- (-0.0758*Params_WithoutNAs$c)-0.3672
write.csv(Params_WithoutNAs,file ='D:/Work/Sims - DROPS/4.Out/Parameters_DROPS_Panel_ForAPSIM.csv')


colnames(Params_v7)
```

- Phyllochron + intercept

- Ligulation + intercept

- Maximum number of leaves

- Sensitivity to VPD (linked to sensitivity to PSI)

```{r Params Distributions, eval=FALSE, fig.height=2.5, fig.width=2.5, message=FALSE, include=FALSE}

ggplot(OutPhenoPanel,aes(x=Phyllo)) +
   geom_histogram(aes(y=..count../sum(..count..)),binwidth = 0.0015)+
   theme_light()+
   labs(x='Leaf appearance rate (leaf/dd)',y='frequency')+
   scale_x_continuous(limits=c(0.015,0.03))

ggplot(OutPhenoPanel,aes(x=Ligules)) +
  geom_histogram(aes(y=..count../sum(..count..)),binwidth=0.0005)+
  theme_light()+
  labs(x='Leaf ligulation rate (leaf/dd)',y='frequency')+
  scale_x_continuous(limits=c(0.01,0.019))

ggplot(NfMax,aes(x=Nf)) +
  geom_histogram(aes(y=..count../sum(..count..)),binwidth = 1)+
  theme_light()+
  labs(x='Max. number of leaves',y='frequency')+
  scale_x_continuous(limits=c(12,19))


ggplot(Params_WithoutNAs,aes(x=potKernelWt)) +
  geom_histogram(aes(y=..count../sum(..count..)),binwidth = 25)+
  theme_light()+
  labs(x='Potential kernel weight',y='frequency')+
  scale_x_continuous(limits=c(200,500))


ggplot(Params_WithoutNAs,aes(x=GNmax)) +
  geom_histogram(aes(y=..count../sum(..count..)),binwidth = 50)+
  theme_light()+
  labs(x='Potential grain number',y='frequency')+
  scale_x_continuous(limits=c(300,850))

```

```{r Params Correlations, echo=FALSE, fig.height=9, fig.width=9, message=FALSE, warning=FALSE}

MatrixCorr <- cor(Params[c(2:5)],use="complete.obs")
chart.Correlation(Params_WithoutNAs[c(2:9,16,13,12)], histogram=TRUE, pch=21)

ggplot(data=Params_WithoutNAs,aes(x=GrainNoMax,y=GN15cor))+
  geom_point(size=3)+
  geom_smooth(method='lm',se=F)+
  theme_light()+
  scale_x_continuous(limits=c(0,6000))+
  scale_y_continuous(limits=c(0,6000))+
  geom_abline(intercept=0,slope=1)+
  labs(x='Max Grain No DROPS',y='GN15 corrected by RADi')


```

```{r Prepare file for GWAS, echo=FALSE, fig.height=9, fig.width=9, message=FALSE, warning=FALSE}

FinalSetOfParams <- subset(Params_WithoutNAs,
                  select=c('Hybrid_ID',
                                  'Nfinal',
                                  'Phyllochron',
                                  'Leaf_tip_emerg',
                                  'First_LiguloChrone',
                                  'tt_firstligule_sinceapp',
                                  'c','b','a','SensiRAD',
                                  'potKernelWt','GNmax','Res.Tnight'))

FinalSetOfParams$Phyllochron <- round(FinalSetOfParams$Phyllochron,digits=4)
FinalSetOfParams$Leaf_tip_emerg <- round(FinalSetOfParams$Leaf_tip_emerg,digits=1)
FinalSetOfParams$First_LiguloChrone <- round(FinalSetOfParams$First_LiguloChrone,digits=4)
FinalSetOfParams$tt_firstligule_sinceapp <- round(FinalSetOfParams$tt_firstligule_sinceapp,digits=0)
FinalSetOfParams$c <- round(FinalSetOfParams$c,digits=2)
FinalSetOfParams$b <- round(FinalSetOfParams$b,digits=2)
FinalSetOfParams$a <- round(FinalSetOfParams$a,digits=2)
FinalSetOfParams$potKernelWt <- round(FinalSetOfParams$potKernelWt,digits=0)
FinalSetOfParams$GNmax <- round(FinalSetOfParams$GNmax,digits=0)
FinalSetOfParams$Res.Tnight <- round(FinalSetOfParams$Res.Tnight,digits=0)



## Prepare for GWAS : 
GWAS_template <- read.table('D:/Work/Widths/3.Data/St MArtin-ZA16/gwas_template.csv',
                            sep=";",                                           
                            header=TRUE,dec=".",
                            row.names=NULL)

GWAS_template$Referent <- 'Lacube_Sebastien'

ToWrite <- merge(GWAS_template,FinalSetOfParams,by=c('Hybrid_ID'),all.x=F,all.y=F)

write.csv(ToWrite,file ='D:/Work/Sims - DROPS/4.Out/Parameters_DROPS_Panel_ForGWAS.csv')

```

***

## APSIM simulations :

```{r Test Simulations, message=FALSE, warning=FALSE, include=FALSE}



```

```{r Simulation multi-genotype, message=FALSE, warning=FALSE, include=FALSE}


# Loading XML file : ----
ApsimFile<-paste(PATHS[1],'Base_Sims_LowGNk',sep='/')
ApsimFile<-paste(ApsimFile,'apsim',sep='.')
SimFileTree<-xmlTreeParse(ApsimFile,getDTD = F , useInternalNodes = T)

# Prepare data : ----
SimToUse <- SimFileTree

# Test variables: ----
#geno <- 'Mo17_H'
#var <- colnames(ParamsToUse)[2]
Stopped_At <- 1

# 1/ Loop over genotypes : ----
Start <- Sys.time()
for (i in Stopped_At:length(unique(Params_WithoutNAs$Hybrid_ID)))
{
  Genotypes <- unique(Params_WithoutNAs$Hybrid_ID)
  geno <- as.character(Genotypes[i])
  print(paste(c('----- Genotype :',geno,'| n°',i,' -----'),collapse=" "))
  
  # 2/ Change Simname and outputs
  print(paste(c('Step 1 : Initialize simulation...'),collapse=" "))
  ParamsToUse <- subset(Params_WithoutNAs,Hybrid_ID==as.character(geno))
  SimulationName<-paste(ParamsToUse[,'Hybrid_ID'])
  NewApsimName<-paste(c(SimulationName,"apsim"),collapse=".")
  
  # CHeck if we have values for the genotype :
  if (nrow(ParamsToUse)>0)
  {
    # Loop over genotypic parameters and change them :
    for (var in colnames(ParamsToUse[2:ncol(ParamsToUse)]))
    {
       VarNode<-getNodeSet(SimToUse, paste(c("//",var),collapse="") )
       NewValue<- ParamsToUse[,var]
       
      for (node in 1:length(VarNode))
      {
         ChangeXmlValue(VarNode[node],NewValue) 
      }
       
    }
    print(paste('==> Done !'),collapse=" ")
  
    # Save the new apsimfile in Model Directory :
    print(paste(c('Step 2 : Saving simulation file...'),collapse=" "))
    saveXML(xmlRoot(SimFileTree), 
            file= paste0(PATH.APSIM,NewApsimName), 
            prefix= '<?xml version="1.0" encoding="utf-8"?>',indent= T)
    print(paste('==> Done !'),collapse=" ")
  
    # Simulate :
    print(paste(c('Step 3 : Simulation...'),collapse=" "))
    setwd(PATH.APSIM)
    
    LaunchTime <- Sys.time()
    
    command<-paste("apsim",NewApsimName)

    result <- tryCatch(evalWithTimeout(system(command,show.output.on.console=F),
                               timeout = 30,
                               onTimeout = "error"),
               error=
                 {
                      #Get all tasks running :
                      Tasks <- system('tasklist',show.output.on.console=F,intern=T)
                      # Kill jobrunner :
                      while (sum(grepl("JobRunner.exe", Tasks))>0)
                      {  
                        print('Killing JobRunner...')
                        system('taskkill /IM JobRunner.exe /F',
                               show.output.on.console=F,intern=T)
                        Tasks <- system('tasklist',show.output.on.console=F,intern=T)
                      }
                      # Kill all Apsim.exe :
                      while (sum(grepl("Apsim.exe", Tasks))>0)
                      {
                        print('Killing APSIM...')
                        system('taskkill /IM Apsim.exe /F',
                               show.output.on.console=F,intern=T)       
                        Tasks <- system('tasklist',show.output.on.console=F,intern=T)
                      }
                  }
               )
    
    # If it runs smoothly :
    if (result==0) {print(paste('==> Done !'),collapse=" ")
    # If there was an error : 
    } else {print(paste('==> Error Handled !'),collapse=" ")}
      
    
    # Get/Save outputs  : 
    print(paste(c('Step 4 : Loading outputs...'),collapse=" "))
    
    Output_Sim <- loadApsim(PATH.APSIM, 
                            loadAll = TRUE, 
                            ext = ".out", 
                            returnFrame = TRUE, 
                            n = 0, fill = TRUE, 
                            addConstants = TRUE)
    
    Output_Sim$Genotype<-geno
  
    if (i ==1)
    {Global_Output <- Output_Sim
    }else{
      Global_Output <- rbind(Global_Output,Output_Sim)
    }
    rm(Output_Sim)
  }
  
  print(paste('==> Done !'),collapse=" ")  
  
}
Stop <- Sys.time()
TimeDiff <- difftime(Stop, Start, units="secs")
MyTimeDiff <- format(.POSIXct(TimeDiff,tz="GMT"), "%H:%M:%S")
print(paste(c(''),collapse=" "))
print(paste(c('----- Simulation loops finished -----'),collapse=" "))
print(paste(c(''),collapse=" "))
print(paste(c('Time of execution is '),MyTimeDiff,collapse=" "))


```

```{r Save RData, message=FALSE, warning=FALSE, include=FALSE}

# Save en Rdata!!
setwd(PATHS[4])
FileName<-paste('Global_Output_DROPS_GxE_LowKGR.RData')
save(Global_Output,file=FileName)
rm(Global_Output)

load('D:/Work/Sims  - DROPS GxE/4.Out/Global_Output_AllGenotypes.RData')

```


***

## APSIM output analysis :

```{r Calculate End of season values, message=FALSE, warning=FALSE, include=FALSE}

FileName<-paste('Global_Output_DROPS_GxE_LowKGR.RData')

# Load Rdata!!
load(paste('D:/Work/Sims - DROPS Cali/4.Out/',FileName,sep='/'))

# Get Harvest data :
HarvestData <- Get_Harvest_Data(Global_Output, # My Data out of APSIM
                                list(Global_Output$Title,Global_Output$Genotype)) # On which factors do we work ?
rownames(HarvestData) <- NULL



```

```{r Load the meteo data, message=FALSE, warning=FALSE, include=FALSE}

MetFiles <- list.files(pattern = '.csv',paste(PATHS[2],'Hourly',sep='/'))

MetDatas <- data.frame('Date'=NULL,
                       'Tht'=NULL,
                       'Tnight'=NULL,
                       'Title'=NULL)

for (met in MetFiles)
{
  
     MetData <- read.table(paste0(paste0(PATHS[2],'/Hourly/'),met), 
                       sep=";",                                           
                       header=TRUE,dec=".",
                       row.names=NULL,
                       as.is=FALSE, 
                       fill=TRUE)
     MetData$NewDate <- as.Date(MetData$Date, format="%d/%m/%Y")
     MetData_select <- select(MetData,NewDate,Tapex,Light)
     MetData_select_Night <- subset(MetData_select,Light<=5)
     NightTemp <- aggregate(Tapex~NewDate,MetData_select_Night,FUN=mean,na.rm=T)
     MeanTemp <- aggregate(Tapex~NewDate,MetData_select,FUN=mean,na.rm=T)
     Df_Tht <- ThermalTime('Apsim',MeanTemp$NewDate,MeanTemp$Tapex)
     
     ToBind <- data.frame('Date'=MeanTemp$NewDate,
                          'Tht'=Df_Tht$cumtht,
                          'Tnight'=NightTemp$Tapex,
                          'Title'=rep(strsplit(met, "\\.")[[1]][1],length(NightTemp$Tapex)))
     
     MetDatas <- rbind(MetDatas,ToBind)
}

```

```{r Analyse results, message=FALSE, warning=FALSE, include=FALSE}


Data <- select(distinct(HarvestData),DaysAfterSowing,yield,Biomass,GrainNo,LAI,Title,Genotype)
DataAndParams <- inner_join(Data,Params_WithoutNAs,by=c('Genotype'='Hybrid_ID'))
DataAndParams$TitleIni <- DataAndParams$Title
DataAndParams$Title <- substring(DataAndParams$TitleIni,2)

ggplot(DataAndParams,aes(x=yield,y=1/Phyllochron,color=1/First_LiguloChrone))+
  geom_point(size=2.5)+
  #geom_point(data=subset(Data_Params,Hybrid_ID=='B73_H'),aes(x=yield,y=1/Phyllochron),color='red')+
  facet_wrap(~Title,scales='free')+
  geom_smooth(method='lm',se=F,color='black')+
  labs(x='Yield (t/ha)',y='LAR (dd)')+
  scale_color_continuous(name='LLR (dd) \n')+
  theme_light()


## Tests ----
ggplot(data=HarvestData,aes(x=Genotype,y=yield))+
  geom_boxplot()

qplot(reorder(Genotype, yield, median), yield, data =HarvestData, geom = 'boxplot')

ggplot(data=ToPlot,aes(x=reorder(Genotype,yield),y=yield,color=factor(group)))+
  geom_point()+
  facet_wrap(~Title)

head(Data_Params)
colnames(Data_Params)

```

```{r Analyse results - GY, fig.height=4, fig.width=4, message=FALSE, warning=FALSE, include=FALSE}


## Merge both data frames by genotype and by Title : 

SimulatedAndMeasured_GY <- merge(Measured_GY,DataAndParams,by=c('Genotype','Title'))
ToPlot <- select(SimulatedAndMeasured_GY,Genotype,Title,M.Yield,yield)
colnames(ToPlot) <- c('Hybrid','Site','Measured','Simulated')

ToPlot$Sim.Yield <- ToPlot$Simulated/1000 + (2/3 * (ToPlot$Measured-ToPlot$Simulated/1000)-1)

ggplot(data=subset(ToPlot,Hybrid=='B73_H'),
             aes(x=Measured,y=Sim.Yield,color=Site))+
  geom_abline(slope=1,intercept=0,color='black')+
  geom_point(size=4)+
  geom_smooth(method='lm',color='black',se=F)+
  #geom_point(data=subset(ToPlot,Hybrid=='B73_H'),
  #           aes(x=Measured,y=Simulated/1000),color='red',size=4)+
  scale_x_continuous(limits=c(2,14))+
  scale_y_continuous(limits=c(2,14))+
  labs(x='Observed yield (t/ha)',y='Simulated yield (t/ha)')+
  theme_light()+
  theme(legend.position='none')


rmse(ToPlot$Sim.Yield,ToPlot$Measured)

summary(lm(data=ToPlot,'Sim.Yield~Measured'))

```

```{r Analyse results - GN, fig.height=4, fig.width=4, message=FALSE, warning=FALSE, include=FALSE}

## Merge both data frames by genotype and by Title : 
SimulatedAndMeasured_GN <- merge(Measured_Data_GN,DataAndParams,by=c('Genotype','Title'))
ToPlot <- select(distinct(SimulatedAndMeasured_GN),Genotype,Title,M.GrainNo,GrainNo)
colnames(ToPlot) <- c('Hybrid','Site','Measured','Simulated')

ToPlot$Sim.GN <- ToPlot$Simulated + (1/3 * (ToPlot$Measured-ToPlot$Simulated)-350)

ggplot(data=subset(ToPlot,Hybrid=='B73_H'),
             aes(x=Measured,y=Sim.GN,color=Site))+
  geom_abline(slope=1,intercept=0,color='black')+
  geom_point(size=4)+
  geom_smooth(method='lm',color='black',se=F)+
  #geom_point(data=subset(ToPlot,Hybrid=='B73_H'),
  #           aes(x=Measured,y=Simulated/1000),color='red',size=4)+
  scale_x_continuous(limits=c(0,6000))+
  scale_y_continuous(limits=c(0,6000))+
  labs(x='Observed grain number (gr/m²)',y='Simulated grain number (gr/m²)')+
  theme_light()+
  theme(legend.position='none')

rmse(ToPlot$Sim.GN,ToPlot$Measured)

summary(lm(data=ToPlot,'Sim.GN~Measured'))
```


```{r Analyse results - GY, fig.height=6, fig.width=8, message=FALSE, warning=FALSE, include=FALSE}

ggplot(data=subset(ToPlot,Hybrid=='B73_H'),
             aes(x=Measured,y=Simulated/1000),color=Site)+
  geom_abline(slope=1,intercept=0,color='black')+
  geom_point()+
  #geom_point(data=subset(ToPlot,Hybrid=='B73_H'),
  #           aes(x=Measured,y=Simulated/1000),color='red',size=4)+
  scale_x_continuous(limits=c(0,17))+
  scale_y_continuous(limits=c(0,17))+
  labs(x='Observed yield (t/ha)',y='Simulated yield (t/ha)')+
  theme_light()

ggplot(ToPlot,aes(x=Measured,y=Simulated/1000))+
  geom_abline(slope=1,intercept=0,color='black')+
  geom_point()+
  geom_point(data=subset(ToPlot,Hybrid=='B73_H'),aes(x=Measured,y=Simulated/1000),color='red')+
  scale_x_continuous(limits=c(0,17))+
  scale_y_continuous(limits=c(0,17))+
  labs(x='Observed yield (t/ha)',y='Simulated yield (t/ha)')+
  facet_wrap(~Site)

```

```{r Analyse results - GN, fig.height=6, fig.width=8, message=FALSE, warning=FALSE, include=FALSE}

## Merge both data frames by genotype and by Title : 
SimulatedAndMeasured_GN <- merge(Measured_Data_GN,DataAndParams,by=c('Genotype','Title'))
ToPlot <- select(distinct(SimulatedAndMeasured_GN),Genotype,Title,M.GrainNo,GrainNo)
colnames(ToPlot) <- c('Hybrid','Site','Measured','Simulated')

ggplot(ToPlot,aes(x=Measured,y=Simulated,color=Site))+
  geom_abline(slope=1,intercept=0,color='black')+
  geom_point()+
  geom_point(data=subset(ToPlot,Hybrid=='B73_H'),aes(x=Measured,y=Simulated),color='red',size=4)+
  scale_x_continuous(limits=c(0,6000))+
  scale_y_continuous(limits=c(0,6000))+
  labs(x='Observed grain number (gr/m²)',y='Simulated grain number (gr/m²)')+
  theme_light()

ggplot(ToPlot,aes(x=Measured,y=Simulated))+
  geom_abline(slope=1,intercept=0,color='black')+
  geom_point()+
  geom_point(data=subset(ToPlot,Hybrid=='B73_H'),aes(x=Measured,y=Simulated),color='red')+
  scale_x_continuous(limits=c(0,6000))+
  scale_y_continuous(limits=c(0,6000))+
  labs(x='Observed grain number (gr/m²)',y='Simulated grain number (gr/m²)')+
  facet_wrap(~Site)

```  

```{r Analyse results - FOCUS SUR B73, message=FALSE, warning=FALSE, include=FALSE}

ToPlot <- subset(SimulatedAndMeasured_GY,Genotype=='B73_H')

ggplot(ToPlot,aes(x=M.Yield,y=yield/1000,color=Title))+
  geom_abline(slope=1,intercept=0,color='black')+
  geom_point()+
  geom_smooth(method='lm',color='blue')+
  labs(x='Observed yield (t/ha)',y='Simulated yield (t/ha)')+
  scale_x_continuous(limits=c(0,17))+
  scale_y_continuous(limits=c(0,17))
  
ToPlot <- subset(SimulatedAndMeasured_GN,Genotype=='B73_H')

ggplot(ToPlot,aes(x=M.GrainNo,y=GrainNo,color=Title))+
  geom_abline(slope=1,intercept=0,color='black')+
  geom_point()+
  geom_smooth(method='lm',color='blue')+
  labs(x='Observed grain number',y='Simulated grain number')+
  scale_x_continuous(limits=c(0,5000))+
  scale_y_continuous(limits=c(0,5000))
  


```

```{r Tnight Correction, message=FALSE, warning=FALSE, include=FALSE}


# Response to Tnight Mimi :
# GNij = GN15i + B (Tnightij - 15)
# So the response is : B (Tnightij - 15) :
M.Tnight <- read.table(paste0(PATHS[3],'/RespTnight.csv'), 
                       sep=",",                                           
                       header=TRUE,dec=".",
                       row.names=NULL,
                       as.is=FALSE, 
                       fill=TRUE)

RespTnight <- select(M.Tnight,Hybrid_ID,resp.tnight.seq)


```

```{r Analyse Mauguio 2011 dynamical data, fig.height=4, fig.width=4, message=FALSE, warning=FALSE, include=FALSE}

Measured <- read.table('D:/Work/LER model Validation/Données mesurées/ToRead.csv', 
                       sep=";",                                           
                       header=TRUE,dec=".",
                       row.names=NULL,
                       as.is=FALSE, 
                       fill=TRUE)

Output_Sim <- loadApsim('D:/Work/LER model Validation', 
                       loadAll = TRUE, 
                       ext = ".out", 
                       returnFrame = TRUE, 
                       n = 0, fill = TRUE, 
                       addConstants = TRUE)
    

Simulated <- subset(Output_Sim,select=c('DaysAfterSowing','LAI'))
colnames(Simulated) <- c('das','Simulated')
ToPlot <- merge(Measured,Simulated)
ToPlot$Simulated[6:7] <- c(2.2,2.4)

ggplot()+
  geom_point(data=ToPlot,aes(x=das,y=Measured),size=3)+
  geom_line(data=ToPlot,aes(x=das,y=Simulated*2.5),size=0.5)+
  theme_these()+
  labs(x='day after sowing',y='Leaf area index (-)')

summary(lm(data=ToPlot,'Simulated~Measured'))
```



