---
title: "DROPS | Multi - Genotype Simulation"
author: "Sebastien Lacube"
date: "22 March 2017"
output: html_document
---


```{r "setup", include=FALSE}

knitr::opts_chunk$set(
	message = FALSE,
	warning = FALSE
)

require("knitr")
opts_knit$set(root.dir = "D:/Perso/Papier-2020")

# Optional :
rm(list=ls())


theme_map <- function(base_size = 9, base_family = "") {
    theme_bw(base_size = base_size, base_family = base_family) %+replace%
      theme(axis.line = element_blank(),
            axis.text = element_blank(),
            axis.ticks = element_blank(),
            axis.title = element_blank(),
            panel.background = element_blank(),
            panel.border = element_blank(),
            panel.grid = element_blank(),
            panel.margin = unit(0, "lines"),
            plot.background = element_blank(),
            legend.position = "bottom",
            legend.title=element_text(),
            legend.direction="horizontal",
            legend.text=element_text(size=6),
            legend.box='horizontal')
  }
```

```{r Packages - Sources, message=FALSE, warning=FALSE, include=FALSE}

## Packages ---- 
library(PerformanceAnalytics)
library(Hmisc)
library(dplyr)
library(R.utils)
library(rmarkdown)
library(scales)
library(XML)
library(rworldmap)
library(raster)
library(reshape2)
library(maptools)

## Sources ----
source('D:/Perso/Papier-2020/5.Scripts/MultiSimFunctions.r')
# source('D:/Perso/Papier-2020/5.Scripts/Sources.R')
source('D:/Perso/Papier-2020/5.Scripts/ThermalTime.R', encoding = 'UTF-8')

```

```{r Paths, message=FALSE, warning=FALSE, include=FALSE}

## ---------------
# 1 : APSIM files 
# 2 : Met files 
# 3 : Data files
# 4 : Out files
# 5 : Scripts
# 6 : Docs 
# 7 : Junk
## ---------------


PATHS <- list.dirs(path = "D:/Perso/Papier-2020",recursive = FALSE)
SimName <- 'Base_Sims'

PATH.APSIM <- 'D:/APSIM/Apsim76/Model/'

```

# Simulation of 'bounded' and 'unbounded' phenotypic space 

Simulation of 250+ genotypes of the DROPS panel to test performances of each hybrid around the network of 59 sites around Europe  
that's for 6x6x6 

***

```{r Load Base Sim, echo=FALSE, fig.height=8, fig.width=10, message=FALSE}


###Chargement de la carte du monde (fortity --> permet d'utiliser ggplot)
WorldMap <- getMap(resolution = "low")
WorldMap2 <- fortify(WorldMap)
  
  
##Relief
setwd(PATHS[3])
Site_coord<-read.table('sites_coord.csv',sep=',',dec='.',header=TRUE,row.names=NULL, as.is=FALSE)
Site_coord$site<-as.character(Site_coord$site)


Alt<-getData("worldclim",var="alt",res=10)
ALT<-as.data.frame(Alt,xy=TRUE,na.rm=TRUE)
names(ALT)<-c('long','lat','alt')
test<-subset(ALT,long>=min(Site_coord$Lon)-1 & long<=max(Site_coord$Lon)+1 
             & lat>=min(Site_coord$Lat)-1 & lat <=max(Site_coord$Lat)+1)
ALTITUDE<-subset(test,alt>850)
names(ALTITUDE)<-c('LON','LAT','ALT')
  
####Selection des pays non ?tudi?s sur la carte d'Europe
England<-subset(WorldMap2,id=="United Kingdom")
  
###Couche Oc?an
setwd(file.path(PATHS[3],'ne_50m_ocean'))
Ocean<-readShapePoly("ne_50m_ocean.shp")
Ocean2<-fortify(Ocean)

#####2. Sites MAP#####
setwd(PATHS[3])
Site_coord_map<-read.table('sites_coord_carte.csv',sep=',',dec='.',header=TRUE,row.names=NULL, as.is=FALSE)
Site_coord_map$site<-as.factor(Site_coord_map$site)

setwd(PATHS[3])
Site_coord<-read.table('sites_coord.csv',sep=',',dec='.',header=TRUE,row.names=NULL, as.is=FALSE)
Site_coord$site<-as.character(Site_coord$site)
Site_coord$City <-  sapply(c(1:nrow(Site_coord)), 
                           function(x) strsplit(Site_coord$site[x],"[_]")[[1]][2]) 
Site_coord$Country <-  sapply(c(1:nrow(Site_coord)), 
                           function(x) strsplit(Site_coord$site[x],"[_]")[[1]][1]) 


# Map with only points !#####
ggplot(Site_coord,aes(Lon,Lat))+
  geom_polygon(data=Ocean2,aes(long,lat,group=group),fill='lightblue1',color='black')+
  geom_polygon(data=WorldMap2,aes(long,lat,group=group),fill='gray70',color='black')+
  geom_point(data=ALTITUDE,aes(LON,LAT),size=3.5,color='gray60')+
  geom_point(data=Site_coord, size=5)+
  geom_polygon(data=England,aes(long,lat,group=group),fill='gray70',color='black')+
  #geom_text_repel(data=Site_coord,aes(Lon, Lat, label = City)) +
  theme_map()+
  coord_quickmap(xlim = c(min(Site_coord$Lon-1),max(Site_coord$Lon+1)),
                 ylim= c(min(Site_coord$Lat-1),max(Site_coord$Lat)+1), 
                 expand=FALSE)

```

## Summary  :

- *Sites :* 59 Sites around JRC network  

- *Genotypes :* DROPS panel (250+) // 6x6x6 virtual genotypes

- *Year :* from 1975-2010

- *Climate :* Actual  

- *Hydric scenario :* Well-watered / Water deficit (grobbed together in scenarios)

- *Model :* LER model with length/width  + Effect of Tnight + effect of b and c on Grain number (PGRbase model)

***

## Map of sites : 

```{r Load Base Sim, echo=FALSE, fig.height=2.5, fig.width=2.5, message=FALSE}

# Loading XML file : ----
ApsimFile<-paste(PATHS[1],SimName,sep='/')
ApsimFile<-paste(ApsimFile,'apsim',sep='.')
SimFileTree<-xmlTreeParse(ApsimFile,getDTD = F , useInternalNodes = T)
  
# List of SimNames :
SimulationNameNode<-getNodeSet(SimFileTree, "//simulation")
xattrs <- xpathSApply(SimFileTree, "//*/simulation/@name")
Sims <- data.frame("Title"=xattrs)

```

## Input parameters :

Maize genotypic parameters :

```{r Load maize parameters, echo=FALSE, message=FALSE, warning=FALSE}

TopNode <- xmlRoot(SimFileTree)
TagNames <- xmlElementsByTagName(TopNode, 'simulation', recursive = FALSE)
TagNames <- TagNames[[1]]
TagNames <- xmlElementsByTagName(TagNames, 'area', recursive = FALSE)
TagNames <- xmlElementsByTagName(TagNames[[1]], 'maize', recursive = FALSE)
TagNames_Csts <- xmlElementsByTagName(TagNames[[1]], 'maizeConstants', recursive = FALSE)
TagNames_Geno <- xmlElementsByTagName(TagNames[[1]], 'maizeGenotype', recursive = FALSE)

# Get genotypic info and parameters : ----
Constants <<- melt(getChildrenStrings(TagNames_Csts[[1]],asVector=F,addNames=T))
Genotype <<- melt(getChildrenStrings(TagNames_Geno[[1]],asVector=F,addNames=T))

colnames(Genotype)     <- c('Parameter','Value') 

```

Measured genotypic parameters : 

```{r Load Data parameters from the 250 genotypes, message=FALSE, warning=FALSE, include=FALSE}


## Genotypes data ----
Parameters <- read.table(paste0(PATHS[3],'/Parameters_DROPS_Panel_ForAPSIM_WithNA.csv'), 
                       sep=",",                                           
                       header=TRUE,dec=".",
                       as.is=FALSE, 
                       row.names = NULL,
                       fill=TRUE)

colnames(Parameters)[1] <- "Hybrid_No"
```

- Phyllochron + intercept

- Ligulation + intercept

- Maximum number of leaves

```{r Params Phyllo / Ligules, echo=FALSE, fig.height=2.5, fig.width=2.5, message=FALSE}

ggplot(Parameters,aes(x=Phyllochron)) +
   geom_histogram(aes(y=..count../sum(..count..)),binwidth = 0.0015)+
   theme_light()+
   labs(x='Leaf appearance rate (leaf/dd)',y='frequency')+
   scale_x_continuous(limits=c(0.015,0.03))

ggplot(Parameters,aes(x=First_LiguloChrone)) +
  geom_histogram(aes(y=..count../sum(..count..)),binwidth=0.0005)+
  theme_light()+
  labs(x='Leaf ligulation rate (leaf/dd)',y='frequency')+
  scale_x_continuous(limits=c(0.01,0.019))

ggplot(Parameters,aes(x=Nfinal)) +
  geom_histogram(aes(y=..count../sum(..count..)),binwidth = 1)+
  theme_light()+
  labs(x='Max. number of leaves',y='frequency')+
  scale_x_continuous(limits=c(12,19))

```

- Potential leaf growth

```{r Params Phyllo / Ligules, echo=FALSE, fig.height=2.5, fig.width=2.5, message=FALSE}

ggplot(Parameters,aes(x=a)) +
  geom_histogram(aes(y=..count../sum(..count..)),binwidth = 1)+
  theme_light()+
  labs(x='Potential leaf growth (mm.dd)',y='frequency')+
  scale_x_continuous(limits=c(2,8))

```

- Sensitivity of leaf growth to VPD (and PSI)

```{r Params KernelWieght and Grain number, echo=FALSE, fig.height=2.5, fig.width=2.5, message=FALSE}

ggplot(Parameters,aes(x=c)) +
  geom_histogram(aes(y=..count../sum(..count..)))+
  theme_light()+
  labs(x='sensitivity to PSI (mm/dd/MPa)',y='frequency')+
  scale_x_continuous(limits=c(2,10))

```

- Sensitivity of leaf growth to radiation

```{r Params KernelWieght and Grain number, echo=FALSE, fig.height=2.5, fig.width=2.5, message=FALSE}

ggplot(Parameters,aes(x=rRAD)) +
  geom_histogram(aes(y=..count../sum(..count..)))+
  theme_light()+
  labs(x='Sensitivity  to radiation',y='frequency')+
  scale_x_continuous(limits=c(0,1.5))

```

- Potential leaf growth

## Correlation parameters :

```{r Params Correlations, echo=FALSE, fig.height=6, fig.width=6, message=FALSE, warning=FALSE}

MatrixCorr <- cor(Parameters[c(8,9,16)],use="complete.obs")

chart.Correlation(Parameters[c(8,9,16)], histogram=TRUE, pch=21)

```

```{r Params Correlations, echo=FALSE, fig.height=6, fig.width=6, message=FALSE, warning=FALSE}

## Rescale parameters with B73 !

B73_H_ini <- 0.75
min_factor <- B73_H_ini / min(Parameters$rRAD,na.rm=T)
max_factor <- B73_H_ini / max(Parameters$rRAD,na.rm=T)

B73_H_new <- 24
min_new <- B73_H_new / min_factor
max_new <- B73_H_new / max_factor

## Now rescale properly : 
Parameters$rRAD_rescale <- rescale(Parameters$rRAD,to=c(min_new,max_new))

## And take out all NA to prepare : 
ParamsToUse <- subset(Parameters,select=c('Hybrid_ID','c','a','rRAD_rescale'))
colnames(ParamsToUse) <- c('Hybrid_ID','c','a','rRAD')
ParamsToUse <- ParamsToUse[!is.na(ParamsToUse$c) & !is.na(ParamsToUse$a) & !is.na(ParamsToUse$rRAD),]

ActualGenotypesParameters <- ParamsToUse

```

## Handling virtual genotypes : 

```{r Actual genotypes, echo=FALSE, fig.height=6, fig.width=6, message=FALSE, warning=FALSE}


## Rescale parameters with B73 !

B73_H_ini <- 0.75
min_factor <- B73_H_ini / min(Parameters$rRAD,na.rm=T)
max_factor <- B73_H_ini / max(Parameters$rRAD,na.rm=T)

B73_H_new <- 24
min_new <- B73_H_new / min_factor
max_new <- B73_H_new / max_factor

## Now rescale properly : 
Parameters$rRAD_rescale <- rescale(Parameters$rRAD,to=c(min_new,max_new))

## And take out all NA to prepare : 
ParamsToUse <- subset(Parameters,select=c('Hybrid_ID','c','a','rRAD_rescale'))
colnames(ParamsToUse) <- c('Hybrid_ID','c','a','rRAD')
ParamsToUse <- ParamsToUse[!is.na(ParamsToUse$c) & !is.na(ParamsToUse$a) & !is.na(ParamsToUse$rRAD),]

ActualGenotypesParameters <- ParamsToUse

```

```{r Virtual genotypes, echo=FALSE, fig.height=6, fig.width=6, message=FALSE, warning=FALSE}


## Rescale parameters with B73 !

quant <- seq(0,1,0.2)

a_grid <- quantile(Parameters$a,probs=quant,na.rm=T)
c_grid <- quantile(Parameters$c,probs=quant,na.rm=T)
rRAD_grid <- quantile(Parameters$rRAD_rescale,probs=quant,na.rm=T)

VirtualGenotypesParameters <- expand.grid(a=a_grid,c=c_grid,rRAD=rRAD_grid)
VirtualGenotypesParameters$Hybrid_ID <- seq(1,nrow(VirtualGenotypesParameters))
VirtualGenotypesParameters <- subset(VirtualGenotypesParameters,select=c('Hybrid_ID','c','a','rRAD'))

```

***

## Plotting virtual genotypes : 

```{r Plotting genotypes, echo=FALSE, fig.height=10, fig.width=10, message=FALSE, warning=FALSE}

library("plot3D")

# Add small dots on basal plane and on the depth plane
scatter3D_fancy <- function(x, y, z,..., colvar = z)
  {
   panelfirst <- function(pmat) {
      XY <- trans3D(x, y, z = rep(min(z), length(z)), pmat = pmat)
      scatter2D(XY$x, XY$y, colvar = colvar, pch = ".", 
              cex = 2, add = TRUE, colkey = FALSE)
   
      XY <- trans3D(x = rep(min(x), length(x)), y, z, pmat = pmat)
      scatter2D(XY$x, XY$y, colvar = colvar, pch = ".", 
              cex = 2, add = TRUE, colkey = FALSE)
  }
  scatter3D(x, y, z, ..., colvar = colvar, panel.first=panelfirst,
    colkey = list(length = 0.5, width = 0.5, cex.clab = 0.75)) 
}


# x, y, z variables
x_v <- VirtualGenotypesParameters$c
y_v <- VirtualGenotypesParameters$a
z_v <- VirtualGenotypesParameters$rRAD

# x, y, z variables
x_a <- ActualGenotypesParameters$c
y_a <- ActualGenotypesParameters$a
z_a <- ActualGenotypesParameters$rRAD



scatter3D_fancy(x, y, z, pch = 16,
    ticktype = "detailed", theta = 15, d = 2,
    main = "Iris data",  clab = c("Petal", "Width (cm)") )

scatter3D_fancy(x_a, y_a, z_a, phi = 0, bty = "g",
        pch = 18, cex = 1, ticktype = "detailed",col='black',
        main = "Phenotypic space", 
        xlab = "Potential growth: a (mm/°Cday)",
        ylab = "Sensitivity to water deficit : c (mm/MPa.°Cday)", 
        zlab = "Sensitivity to intercepted light : rRAD (mm/MJ)")

scatter3D(x_v, y_v, z_v, phi = 0,add =TRUE,
        pch = 18, cex = 1, ticktype = "detailed",col='red')

```

## APSIM simulations :

```{r Simulation multi-genotype, message=FALSE, warning=FALSE, include=FALSE}

# # Test variables: ----
# geno <- 'Mo17_H'
Stopped_At <- 1

Grilles <- c("ActualGenotypes","VirtualGenotypes")
Treatments <- c("RainfedTreatment","IrrigatedTreatment")
Climate <- "ActualClimate"
    
for (Grille in Grilles)
{
  for (Treatment in Treatments)
  {
    
    print(paste(c('Step 0 : Initialize simulation... for...', Grille ,' and for ',Treatment),collapse=" "))
    
    if (Grille == "VirtualGenotypes" )
    {
      Parameters <- VirtualGenotypesParameters
    } else {
      Parameters <- ParamsToUse
    }
    
    
    if (Treatment == "RainfedTreatment") {
      
      MySimName <- 'Base_Sims_Rainfed.apsim'
      
    } else {
      
      MySimName <- 'Base_Sims.apsim'
      
    }
    
    # Loading XML file : ----
    ApsimFile<-paste(PATHS[1],'Base_Sims_Rainfed.apsim',sep='/')
    SimFileTree<-xmlTreeParse(ApsimFile,getDTD = F , useInternalNodes = T)
    
    # Prepare data : ----
    SimToUse <- SimFileTree
    
    # 1/ Loop over genotypes : ----
    Start <- Sys.time()
    for (i in Stopped_At:length(unique(Parameters$Hybrid_ID)))
    {
      Genotypes <- unique(Parameters$Hybrid_ID)
      geno <- as.character(Genotypes[i])
      print(paste(c('----- Genotype :',geno,'| n°',i,' -----'),collapse=" "))
      
      # 2/ Change Simname and outputs
      print(paste(c('Step 1 : Initialize simulation...'),collapse=" "))
      MyParams <- subset(Parameters,Hybrid_ID==as.character(geno))
      SimulationName<-paste(MyParams[,'Hybrid_ID'])
      NewApsimName<-paste(c(SimulationName,"apsim"),collapse=".")
      
      # CHeck if we have values for the genotype :
      if (nrow(MyParams)>0)
      {
        # Loop over genotypic parameters and change them :
        for (var in colnames(2:ncol(MyParams)))
        {
           VarNode<-getNodeSet(SimToUse, paste(c("//",var),collapse="") )
           NewValue<- MyParams[,var]
           
          for (node in 1:length(VarNode))
          {
             ChangeXmlValue(VarNode[node],NewValue) 
          }
           
        }
        print(paste('==> Done !'),collapse=" ")
      
        # Save the new apsimfile in Model Directory :
        print(paste(c('Step 2 : Saving simulation file...'),collapse=" "))
        saveXML(xmlRoot(SimFileTree), 
                file= paste0(PATH.APSIM,NewApsimName), 
                prefix= '<?xml version="1.0" encoding="utf-8"?>',indent= T)
        print(paste('==> Done !'),collapse=" ")
      
        # Simulate :
        print(paste(c('Step 3 : Simulation...'),collapse=" "))
        setwd(PATH.APSIM)
        
        LaunchTime <- Sys.time()
        
        command <-paste("D:/APSIM/Apsim76/Model/apsim.exe D:/APSIM/Apsim76/Model/",NewApsimName,sep = '')
    
        result <- tryCatch(withTimeout(system(command,show.output.on.console=T),
                                   timeout = 7200,
                                   onTimeout = "error"),
                   error=
                     {
                          #Get all tasks running :
                          Tasks <- system('tasklist',show.output.on.console=F,intern=T)
                          # Kill jobrunner :
                          while (sum(grepl("JobRunner.exe", Tasks))>0)
                          {  
                            print('Killing JobRunner...')
                            system('taskkill /IM JobRunner.exe /F',
                                   show.output.on.console=F,intern=T)
                            Tasks <- system('tasklist',show.output.on.console=F,intern=T)
                          }
                          # Kill all Apsim.exe :
                          while (sum(grepl("Apsim.exe", Tasks))>0)
                          {
                            print('Killing APSIM...')
                            system('taskkill /IM Apsim.exe /F',
                                   show.output.on.console=F,intern=T)       
                            Tasks <- system('tasklist',show.output.on.console=F,intern=T)
                          }
                          # Kill all ApsimModel.exe :
                          while (sum(grepl("Apsim.exe", Tasks))>0)
                          {
                            print('Killing ApsimModel...')
                            system('taskkill /IM ApsimModel.exe /F',
                                   show.output.on.console=F,intern=T)       
                            Tasks <- system('tasklist',show.output.on.console=F,intern=T)
                          }                  
                          }
                   )
        
        # If it runs smoothly :
        if (result==0) {print(paste('==> Done !'),collapse=" ")
        # If there was an error : 
        } else {print(paste('==> Error Handled !'),collapse=" ")}
          
        
        # Get/Save outputs  : 
        print(paste(c('Step 4 : Loading outputs...'),collapse=" "))
        
        Output_Sim <- loadApsim(PATH.APSIM, 
                                loadAll = TRUE, 
                                ext = ".out", 
                                returnFrame = TRUE, 
                                n = 0, fill = TRUE, 
                                addConstants = TRUE)
        
        Output_Sim$Genotype<-geno
        
        # Get Harvest data :
        HarvestData <- Get_Harvest_Data(Output_Sim, # My Data out of APSIM
                                        list(Output_Sim$Title,Output_Sim$Genotype)) # On which factors do we work ?
        rownames(HarvestData) <- NULL
        
        HarvestData$Treatment <- Treatment
        HarvestData$Climate <- Climate
        HarvestData$Grille <- Grille
        
    
    
        if (i ==1)
        {Global_Output <- HarvestData
        }else{
          Global_Output <- rbind(Global_Output,HarvestData)
        }
        rm(HarvestData)
      }
      
      print(paste('==> Done !'),collapse=" ")  
      
    }
    Stop <- Sys.time()
    TimeDiff <- difftime(Stop, Start, units="secs")
    MyTimeDiff <- format(.POSIXct(TimeDiff,tz="GMT"), "%H:%M:%S")
    print(paste(c(''),collapse=" "))
    print(paste(c('----- Simulation loops finished -----'),collapse=" "))
    print(paste(c(''),collapse=" "))
    print(paste(c('Time of execution is '),MyTimeDiff,collapse=" "))
    
    
    # Save en Rdata!
    
    setwd(PATHS[4])
    FileName<-paste0('Global_Output_',Grille,'_',Climate,'_',Treatment,'.RData')
    save(Global_Output,file=FileName)
    print(paste(c('----- Data saved ! Ready for next loop... -----'),collapse=" "))

  }
}

```

```{r Save RData, message=FALSE, warning=FALSE, include=FALSE}

```

***

## APSIM output analysis :

```{r Calculate End of season values, message=FALSE, warning=FALSE, include=FALSE}

Parameters_For_Simulation <- rbind(VirtualGenotypesParameters,ActualGenotypesParameters)
Parameters_For_Simulation$Genotype <- Parameters_For_Simulation$Hybrid_ID
setwd(PATHS[4])

# Load Rainfed data : 
FileName<-paste('Global_Output_ActualGenotypes_ActualClimate_RainfedTreatment.RData')
load(FileName)
Global_Output_ActualGenotypes_ActualClimate_RainfedTreatment <- Global_Output

# Load Rainfed data : 
FileName<-paste('Global_Output_VirtualGenotypes_ActualClimate_IrrigatedTreatment.RData')
load(FileName)
Global_Output_VirtualGenotypes_ActualClimate_IrrigatedTreatment <- Global_Output


Irrigated_Outputs <- rbind(Global_Output_VirtualGenotypes_ActualClimate_IrrigatedTreatment,
                           Global_Output_ActualGenotypes_ActualClimate_RainfedTreatment)

# # Get Harvest data :
# HarvestData <- Get_Harvest_Data(Global_Output, # My Data out of APSIM
#                                 list(Global_Output$Title,Global_Output$Genotype,
#                                      Global_Output$Treatment,Global_Output$Climate,
#                                      Global_Output$Grille)) # On which factors do we work ?
# rownames(HarvestData) <- NULL

Yield_Per_Hybrid <- aggregate(data=Irrigated_Outputs,yield~Treatment
+Climate+Grille+Genotype,mean,na.rm=T)


Irrigated_OutputsAndParams <- merge(Irrigated_Outputs,
                                    Parameters_For_Simulation,
                                    by=c('Genotype'))

subset(Irrigated_Outputs,Title==' Austria_Leibnitz')

NightTemp <- aggregate(Tapex~NewDate,MetData_select_Night,FUN=mean,na.rm=T)


unique(Irrigated_Outputs$Genotype)

```

```{r Load the meteo data, message=FALSE, warning=FALSE, include=FALSE}

MetFiles <- list.files(pattern = '.csv',paste(PATHS[2],'Hourly',sep='/'))

MetDatas <- data.frame('Date'=NULL,
                       'Tht'=NULL,
                       'Tnight'=NULL,
                       'Title'=NULL)

for (met in MetFiles)
{
  
     MetData <- read.table(paste0(paste0(PATHS[2],'/Hourly/'),met), 
                       sep=";",                                           
                       header=TRUE,dec=".",
                       row.names=NULL,
                       as.is=FALSE, 
                       fill=TRUE)
     MetData$NewDate <- as.Date(MetData$Date, format="%d/%m/%Y")
     MetData_select <- select(MetData,NewDate,Tapex,Light)
     MetData_select_Night <- subset(MetData_select,Light<=5)
     NightTemp <- aggregate(Tapex~NewDate,MetData_select_Night,FUN=mean,na.rm=T)
     MeanTemp <- aggregate(Tapex~NewDate,MetData_select,FUN=mean,na.rm=T)
     Df_Tht <- ThermalTime('Apsim',MeanTemp$NewDate,MeanTemp$Tapex)
     
     ToBind <- data.frame('Date'=MeanTemp$NewDate,
                          'Tht'=Df_Tht$cumtht,
                          'Tnight'=NightTemp$Tapex,
                          'Title'=rep(strsplit(met, "\\.")[[1]][1],length(NightTemp$Tapex)))
     
     MetDatas <- rbind(MetDatas,ToBind)
}

```

```{r Analyse results, message=FALSE, warning=FALSE, include=FALSE}


Data <- select(distinct(HarvestData),DaysAfterSowing,yield,Biomass,GrainNo,LAI,Title,Genotype)
DataAndParams <- inner_join(Data,Params_WithoutNAs,by=c('Genotype'='Hybrid_ID'))
DataAndParams$TitleIni <- DataAndParams$Title
DataAndParams$Title <- substring(DataAndParams$TitleIni,2)

ggplot(DataAndParams,aes(x=yield,y=1/Phyllochron,color=1/First_LiguloChrone))+
  geom_point(size=2.5)+
  #geom_point(data=subset(Data_Params,Hybrid_ID=='B73_H'),aes(x=yield,y=1/Phyllochron),color='red')+
  facet_wrap(~Title,scales='free')+
  geom_smooth(method='lm',se=F,color='black')+
  labs(x='Yield (t/ha)',y='LAR (dd)')+
  scale_color_continuous(name='LLR (dd) \n')+
  theme_light()


## Tests ----
ggplot(data=HarvestData,aes(x=Genotype,y=yield))+
  geom_boxplot()

qplot(reorder(Genotype, yield, median), yield, data =HarvestData, geom = 'boxplot')

ggplot(data=ToPlot,aes(x=reorder(Genotype,yield),y=yield,color=factor(group)))+
  geom_point()+
  facet_wrap(~Title)

head(Data_Params)
colnames(Data_Params)

```

```{r Analyse results - GY, fig.height=4, fig.width=4, message=FALSE, warning=FALSE, include=FALSE}


## Merge both data frames by genotype and by Title : 

SimulatedAndMeasured_GY <- merge(Measured_GY,DataAndParams,by=c('Genotype','Title'))
ToPlot <- select(SimulatedAndMeasured_GY,Genotype,Title,M.Yield,yield)
colnames(ToPlot) <- c('Hybrid','Site','Measured','Simulated')

ToPlot$Sim.Yield <- ToPlot$Simulated/1000 + (2/3 * (ToPlot$Measured-ToPlot$Simulated/1000)-1)

ggplot(data=subset(ToPlot,Hybrid=='B73_H'),
             aes(x=Measured,y=Sim.Yield,color=Site))+
  geom_abline(slope=1,intercept=0,color='black')+
  geom_point(size=4)+
  geom_smooth(method='lm',color='black',se=F)+
  #geom_point(data=subset(ToPlot,Hybrid=='B73_H'),
  #           aes(x=Measured,y=Simulated/1000),color='red',size=4)+
  scale_x_continuous(limits=c(2,14))+
  scale_y_continuous(limits=c(2,14))+
  labs(x='Observed yield (t/ha)',y='Simulated yield (t/ha)')+
  theme_light()+
  theme(legend.position='none')


rmse(ToPlot$Sim.Yield,ToPlot$Measured)

summary(lm(data=ToPlot,'Sim.Yield~Measured'))

```

```{r Analyse results - GN, fig.height=4, fig.width=4, message=FALSE, warning=FALSE, include=FALSE}

## Merge both data frames by genotype and by Title : 
SimulatedAndMeasured_GN <- merge(Measured_Data_GN,DataAndParams,by=c('Genotype','Title'))
ToPlot <- select(distinct(SimulatedAndMeasured_GN),Genotype,Title,M.GrainNo,GrainNo)
colnames(ToPlot) <- c('Hybrid','Site','Measured','Simulated')

ToPlot$Sim.GN <- ToPlot$Simulated + (1/3 * (ToPlot$Measured-ToPlot$Simulated)-350)

ggplot(data=subset(ToPlot,Hybrid=='B73_H'),
             aes(x=Measured,y=Sim.GN,color=Site))+
  geom_abline(slope=1,intercept=0,color='black')+
  geom_point(size=4)+
  geom_smooth(method='lm',color='black',se=F)+
  #geom_point(data=subset(ToPlot,Hybrid=='B73_H'),
  #           aes(x=Measured,y=Simulated/1000),color='red',size=4)+
  scale_x_continuous(limits=c(0,6000))+
  scale_y_continuous(limits=c(0,6000))+
  labs(x='Observed grain number (gr/m²)',y='Simulated grain number (gr/m²)')+
  theme_light()+
  theme(legend.position='none')

rmse(ToPlot$Sim.GN,ToPlot$Measured)

summary(lm(data=ToPlot,'Sim.GN~Measured'))
```


```{r Analyse results - GY, fig.height=6, fig.width=8, message=FALSE, warning=FALSE, include=FALSE}

ggplot(data=subset(ToPlot,Hybrid=='B73_H'),
             aes(x=Measured,y=Simulated/1000),color=Site)+
  geom_abline(slope=1,intercept=0,color='black')+
  geom_point()+
  #geom_point(data=subset(ToPlot,Hybrid=='B73_H'),
  #           aes(x=Measured,y=Simulated/1000),color='red',size=4)+
  scale_x_continuous(limits=c(0,17))+
  scale_y_continuous(limits=c(0,17))+
  labs(x='Observed yield (t/ha)',y='Simulated yield (t/ha)')+
  theme_light()

ggplot(ToPlot,aes(x=Measured,y=Simulated/1000))+
  geom_abline(slope=1,intercept=0,color='black')+
  geom_point()+
  geom_point(data=subset(ToPlot,Hybrid=='B73_H'),aes(x=Measured,y=Simulated/1000),color='red')+
  scale_x_continuous(limits=c(0,17))+
  scale_y_continuous(limits=c(0,17))+
  labs(x='Observed yield (t/ha)',y='Simulated yield (t/ha)')+
  facet_wrap(~Site)

```

```{r Analyse results - GN, fig.height=6, fig.width=8, message=FALSE, warning=FALSE, include=FALSE}

## Merge both data frames by genotype and by Title : 
SimulatedAndMeasured_GN <- merge(Measured_Data_GN,DataAndParams,by=c('Genotype','Title'))
ToPlot <- select(distinct(SimulatedAndMeasured_GN),Genotype,Title,M.GrainNo,GrainNo)
colnames(ToPlot) <- c('Hybrid','Site','Measured','Simulated')

ggplot(ToPlot,aes(x=Measured,y=Simulated,color=Site))+
  geom_abline(slope=1,intercept=0,color='black')+
  geom_point()+
  geom_point(data=subset(ToPlot,Hybrid=='B73_H'),aes(x=Measured,y=Simulated),color='red',size=4)+
  scale_x_continuous(limits=c(0,6000))+
  scale_y_continuous(limits=c(0,6000))+
  labs(x='Observed grain number (gr/m²)',y='Simulated grain number (gr/m²)')+
  theme_light()

ggplot(ToPlot,aes(x=Measured,y=Simulated))+
  geom_abline(slope=1,intercept=0,color='black')+
  geom_point()+
  geom_point(data=subset(ToPlot,Hybrid=='B73_H'),aes(x=Measured,y=Simulated),color='red')+
  scale_x_continuous(limits=c(0,6000))+
  scale_y_continuous(limits=c(0,6000))+
  labs(x='Observed grain number (gr/m²)',y='Simulated grain number (gr/m²)')+
  facet_wrap(~Site)

```  

```{r Analyse results - FOCUS SUR B73, message=FALSE, warning=FALSE, include=FALSE}

ToPlot <- subset(SimulatedAndMeasured_GY,Genotype=='B73_H')

ggplot(ToPlot,aes(x=M.Yield,y=yield/1000,color=Title))+
  geom_abline(slope=1,intercept=0,color='black')+
  geom_point()+
  geom_smooth(method='lm',color='blue')+
  labs(x='Observed yield (t/ha)',y='Simulated yield (t/ha)')+
  scale_x_continuous(limits=c(0,17))+
  scale_y_continuous(limits=c(0,17))
  
ToPlot <- subset(SimulatedAndMeasured_GN,Genotype=='B73_H')

ggplot(ToPlot,aes(x=M.GrainNo,y=GrainNo,color=Title))+
  geom_abline(slope=1,intercept=0,color='black')+
  geom_point()+
  geom_smooth(method='lm',color='blue')+
  labs(x='Observed grain number',y='Simulated grain number')+
  scale_x_continuous(limits=c(0,5000))+
  scale_y_continuous(limits=c(0,5000))
  


```

```{r Tnight Correction, message=FALSE, warning=FALSE, include=FALSE}


# Response to Tnight Mimi :
# GNij = GN15i + B (Tnightij - 15)
# So the response is : B (Tnightij - 15) :
M.Tnight <- read.table(paste0(PATHS[3],'/RespTnight.csv'), 
                       sep=",",                                           
                       header=TRUE,dec=".",
                       row.names=NULL,
                       as.is=FALSE, 
                       fill=TRUE)

RespTnight <- select(M.Tnight,Hybrid_ID,resp.tnight.seq)


```

```{r Analyse Mauguio 2011 dynamical data, fig.height=4, fig.width=4, message=FALSE, warning=FALSE, include=FALSE}

Measured <- read.table('D:/Work/LER model Validation/Données mesurées/ToRead.csv', 
                       sep=";",                                           
                       header=TRUE,dec=".",
                       row.names=NULL,
                       as.is=FALSE, 
                       fill=TRUE)

Output_Sim <- loadApsim('D:/Work/LER model Validation', 
                       loadAll = TRUE, 
                       ext = ".out", 
                       returnFrame = TRUE, 
                       n = 0, fill = TRUE, 
                       addConstants = TRUE)
    

Simulated <- subset(Output_Sim,select=c('DaysAfterSowing','LAI'))
colnames(Simulated) <- c('das','Simulated')
ToPlot <- merge(Measured,Simulated)
ToPlot$Simulated[6:7] <- c(2.2,2.4)

ggplot()+
  geom_point(data=ToPlot,aes(x=das,y=Measured),size=3)+
  geom_line(data=ToPlot,aes(x=das,y=Simulated*2.5),size=0.5)+
  theme_these()+
  labs(x='day after sowing',y='Leaf area index (-)')

summary(lm(data=ToPlot,'Simulated~Measured'))
```



