---
title: "DROPS - Water deficit"
author: "Sebastien Lacube"
date: "14 November 2017"
output: html_document
---


```{r Paths, message=FALSE, warning=FALSE, include=FALSE}

## ---------------
# 1 : APSIM files 
# 2 : Met files 
# 3 : Data files
# 4 : Out files
# 5 : Scripts
# 6 : Docs 
# 7 : Junk
## ---------------


PATHS <- list.dirs(path = "D:/Work/Sims  - DROPS GxE",recursive = FALSE)
SimName <- 'Base_Sims'

PATH.APSIM <- 'D:/APSIM/Apsim76/Model/'

```

```{r Sources, fig.height=5, fig.width=6, message=FALSE, warning=FALSE, include=FALSE}


# Libraries ----
library(dplyr)
library(maptools)
library(rworldmap)
library(ggplot2)
library(RColorBrewer)
library(akima)
library(ggmap)
library(rgdal)
library(fields)
library(ggthemes)
library(ggThemeAssist)
library(raster)
library(dismo)
library(ggplot2)
library(RColorBrewer)
library(nlme)
library(gridExtra)
library(reshape2)
library(APSIM)
library(FactoMineR)
library(car)
library(knitr)
library(ggrepel)
library(PerformanceAnalytics)
library(corrplot)
library(devtools)
library(factoextra)
library(plyr)
library(sensitivity)
library(solaR)
library(lubridate)
library(lattice)
library(ReporteRs)
library(Hmisc)
library(scales)
library(ggcorrplot)
library(RSelenium)
library(zoo)
library(maptools)
library(rworldmap)
library(ggplot2)
library(RColorBrewer)
library(akima)
library(ggmap)
library(rgdal)
library(fields)
library(ggthemes)
library(ggThemeAssist)
library(raster)
library(dismo)
library(XML)


# Sources ----
source('D:/Work/R script/APSIM/MultiSimFunctions.r')
source('D:/Work/R script/Sources/Sources.r')
source('D:/Work/R script/Sources/LERmodel.r')
source('D:/Work/R script/Sources/ggplot_smooth_func.R')
source('D:/Work/R script/Sources/ThermalTime.r')
source('D:/Work/R script/Sources/suncourse.r')
source('D:/Work/R script/Sources/PM-FT-function.R')
source('D:/Work/R script/Sources/PM-FAO56-function.r')

# Functions ----
theme_map <- function(base_size = 8, base_family = "") {
  theme_bw(base_size = base_size, base_family = base_family) %+replace%
    theme(axis.line = element_blank(),
          axis.text = element_blank(),
          axis.ticks = element_blank(),
          axis.title = element_blank(),
          panel.background = element_blank(),
          panel.border = element_blank(),
          panel.grid = element_blank(),
          panel.margin = unit(0, "lines"),
          plot.background = element_blank(),
          legend.position = "bottom",
          legend.direction="horizontal",
          legend.title=element_blank(),
          legend.text=element_text(size=8),
          legend.box='horizontal')
}

## Getting all data for harvest dates only (max DAS):
Get_Harvest_Data <- function(Output_Sim,By)
{
  HarvestDateSim <-   
    do.call("rbind",lapply(split(Output_Sim,By,drop=T),
                         function(x)
                         {
                           Temp<-subset(x, DaysAfterSowing==max(x$DaysAfterSowing))
                           return(Temp)
                         }
                       ) ## End lapply
                      ) ## End do.call rbind  
  return(HarvestDateSim)
}

theme_these <- 
  function(base_size = 16, base_family = "") {
  theme_bw(base_size = base_size, base_family = base_family) %+replace%
    theme(panel.background = element_blank(),
          plot.background = element_blank(),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          legend.position = "none",
          legend.direction="horizontal",
          legend.text=element_text(size=16),
          plot.title = element_text(hjust = 0.5,margin = margin(b = + 10)),
          strip.background = element_blank(),
          strip.text.x = element_blank())
  }


```

# Simulation Report


Simulation of 250+ genotypes of the DROPS panel to test performances  
of the model for yield/grain number around the DROPS network.  
  
*Do we simulate correctly DROPS network in Water deficit conditions ?*  

***   

```{r Load Base Sim, echo=FALSE, fig.height=2.5, fig.width=2.5, message=FALSE}

# Loading XML file : ----
ApsimFile<-paste(PATHS[1],SimName,sep='/')
ApsimFile<-paste(ApsimFile,'apsim',sep='.')
SimFileTree<-xmlTreeParse(ApsimFile,getDTD = F , useInternalNodes = T)
  
# List of SimNames : ----
SimulationNameNode<-getNodeSet(SimFileTree, "//simulation")
xattrs <- xpathSApply(SimFileTree, "//*/simulation/@name")
Sims <- data.frame("Title"=xattrs)

```

## Summary  :

- *Sites :* 9 Sites around DROPS network  

- *Genotypes :* DROPS panel (250+)

- *Year :* from 2011 to 2013 

- *Climate :* Actual  

- *Hydric scenario :* Well-watered  

- *Model :* LER model with length/width  

***

